\documentclass[11pt]{article}
\usepackage[margin=0.55in]{geometry}
\usepackage{booktabs}\usepackage{array}\usepackage{enumitem}\usepackage{xcolor}
\setlist{nosep,leftmargin=1.4em}
\renewcommand{\arraystretch}{1.25}
\pagestyle{empty}
\newcolumntype{P}{>{\bfseries}l}
\begin{document}

\begin{center}
{\LARGE\bfseries Tournament NLH Cheat Sheet}\\[2pt]
{\large No-Limit Hold'em \;$\cdot$\; 6--9 handed \;$\cdot$\; raise-or-fold, shove when short}
\end{center}
\vspace{2pt}

\noindent{\large\bfseries 0. Read the format before you sit} \quad\small(this decides everything below)
\begin{itemize}[leftmargin=1.6em]
\item \textbf{Speed.} Blind levels $\le$5 min = \textbf{hyper-turbo}: you go from deep to short in minutes, so \emph{push/fold is your main mode, not the exception}. Be registered from the start for max big blinds.
\item \textbf{Payout = your real goal.} Check the prize tab:
\begin{itemize}[leftmargin=1.3em,label=$\circ$]
\item \textbf{Flat / satellite} (1st $\approx$ min-cash; often only a few \% paid): the \emph{only} goal is to reach the money. \textbf{Far from the bubble $\Rightarrow$ accumulate} --- a short stack has $\approx$0 equity for the top few \%, and in a freeroll busting is free, so take good aggressive +EV spots to build. \textbf{At the bubble $\Rightarrow$ pure survival:} fold everything marginal, let short stacks bust each other, and with a big stack jam into mid stacks that can't call. \textbf{Once you cash, your prize is locked $\Rightarrow$ shove every hand.}
\item \textbf{Top-heavy} (1st $\gg$ min-cash): chips have real value --- play to go deep and win, while still respecting the bubble.
\end{itemize}
\end{itemize}

\vspace{5pt}
\noindent{\large\bfseries Core rules}
\begin{enumerate}[leftmargin=1.6em]
\item \textbf{Raise or fold.} Open to \textbf{2--2.5 bb}; never limp, don't cold-call raises out of position. Not good enough to raise $\Rightarrow$ fold.
\item \textbf{Tighter early, wider late.} Your seat decides how many hands you play --- a handful up front, a ton on the button. \textbf{Antes in play $\Rightarrow$ steal/jam a touch wider} (more dead money to win).
\item \textbf{Your stack picks the mode.} \;\textbf{$>$20 bb} = normal raise/fold. \;\textbf{10--20 bb} = raise small but be ready to jam from late. \;\textbf{$<$10 bb} = shove or fold.
\item \textbf{Don't punt --- scale it to the payout.} You never \emph{need} to flip; accumulate in good spots. The \textbf{flatter the payout and closer the bubble}, the tighter you fold marginal spots and the harder you let short stacks bust each other.
\end{enumerate}

\vspace{6pt}
\noindent{\large\bfseries Opening ranges} \quad\small(raise $\approx$2.2 bb when folded to you; otherwise fold)
\vspace{2pt}

\begin{center}
\begin{tabular}{P p{0.66\textwidth} r}
\toprule
\textbf{Position} & \textbf{Open with} & \%\\
\midrule
Early (UTG/UTG+1) & 77+,\; AQ+,\; AJs+,\; KQs & 8\\
Middle (MP/HJ) & \emph{above} + 55+,\; ATs+,\; KJs+,\; QJs,\; JTs,\; AJo,\; KQo & 13\\
Cutoff & \emph{above} + 22+,\; any suited ace (A2s+),\; suited connectors 54s+,\; KTo,\; QJo & 25\\
Button & any pair,\; any suited ace,\; any two Broadway,\; suited connectors/gappers,\; A2o+,\; K9o+,\; Q9o+ & 45\\
Small blind (folded to you) & $\approx$40\% --- raise, or \textbf{shove} if you're $\le$15 bb & 40\\
\bottomrule
\end{tabular}
\end{center}

\vspace{6pt}
\noindent{\large\bfseries When to shove (open all-in) instead of raise}
\begin{itemize}[leftmargin=1.6em]
\item \textbf{$>$20 bb:} never open-shove --- raise small.
\item \textbf{15--20 bb:} raise small mostly; open-shoving is fine from \textbf{CO / BTN / SB}; \textbf{3-bet shove} premiums over a raise.
\item \textbf{10--15 bb:} \textbf{open-shove is your main move} when folded to you --- tight from early, wide from late.
\item \textbf{$<$10 bb:} \textbf{shove or fold, period.} Jam any decent hand, very wide from late position; don't blind yourself to death.
\item \textbf{3-bet shove (12--22 bb):} someone raises and you hold \textbf{QQ+ / AK} (add JJ/AQ vs a late-position raiser) $\Rightarrow$ jam all-in over them.
\end{itemize}

\vspace{8pt}
\noindent\fbox{\parbox{0.97\linewidth}{\centering
\textbf{In one line:} \;\textbf{Read the payout first} --- flat/satellite $\rightarrow$ survive to the money, then jam everything; top-heavy $\rightarrow$ play to win. \;Then by stack: deep ($>$20 bb) $\rightarrow$ raise-or-fold by position; \;short ($<$15 bb) $\rightarrow$ open-jam late; \;desperate ($<$10 bb) $\rightarrow$ shove or fold.}}

\vspace{6pt}
\noindent\footnotesize\textit{This replaces the all-in/fold sheets, which were for a different game. Facing a raise: fold most hands; continue (or 3-bet/jam) only with strong holdings --- being the aggressor beats calling off.}
\end{document}
